QPLIB: A Library of Quadratic Programming Instances

### 2018-02-08 QPLIB-1.0.tex
update end of intro
- update number of minlplib2 instances
- add question on credibility of mittelmann page
- fix some typos

The structure of this paper is as follows. In \S\ref{sec:QPbasic} we review the basic notion of QP. In particular, \S\ref{subsec:notation} sets out the notation, \S\ref{sec:classification} proposes a new taxonomy of QP that helps us in discussing the (very) different classes of QPs, and \S\ref{sec:algo} very briefly reviews the solution methods for QP and the solvers we have employed.
Next \S\ref{sec:lib} describes the process used to obtain the library and its results.
%; the software tools that we have used, and that are freely released together with the library, are discussed in \S\ref{subsec:tools}.
Some conclusions are drawn in \S\ref{sec:conclusions}, after which Appendix A provides a complete description of all the instances of the library, while Appendix B describes a simple (QPLIB) file format that encodes all of our examples.

While no performance issues of solvers for QP problems are considered in
this paper, we refer to the comprehensive benchmark site \url{http://plato.asu.edu/bench.html}. Of the result on this site, three deal exclusively with
QP problems, namely the (1) large SOCP, (2) MISOCP, and the (3) MIQ(C)P benchmarks, while three others contain have partial results for such problems,
namely those for (4) parallel barrier solvers on large LP/QP problems, (5) AMPL-NLP and (6) MINLP.
Benchmarks (1, 2 \& 4) contain only convex instances, while the others
include nonconvex ones. Global optima are obtained by several of the solvers in
benchmarks (3 \& 5), while all solvers in the latest addition (6) compute
global optima.
%, they are ANTIGONE,
%BARON, COUENNE, LINDO, and SCIP, c.f.~\S\ref{subsec:solver}.
Benchmark (6) is based on MINLPLib~2 \cite{Vigerske2014}, a
collection of currently 1388 instances. In order to give a first representative
impression of solver performance, care was taken there to reduce the number of
instances and allow all solvers to finish in a reasonable time.
More than half of the selected instances are QP or QCP.
%A time limit of two hours on a
%modern workstation with sufficient memory was used. Computations were done in
%GAMS with scripts derived from the SCIP check scripts and available at GitHub.
For details we refer to \url{http://plato.asu.edu/ftp/minlp.html}.

>>>>

The structure of this paper is as follows. In \S\ref{sec:QPbasic} we review the basic notion of QP. In particular, \S\ref{subsec:notation} sets out the notation, \S\ref{sec:classification} proposes a new taxonomy of QP that helps us in discussing the (very) different classes of QPs, and \S\ref{sec:algo} very briefly reviews the solution methods for QP and the solvers we have employed.
Next, \S\ref{sec:lib} describes the process used to obtain the library and its results.
%; the software tools that we have used, and that are freely released together with the library, are discussed in \S\ref{subsec:tools}.
Some conclusions are drawn in \S\ref{sec:conclusions}, after which Appendix A provides a complete description of all the instances of the library, while Appendix B describes a simple (QPLIB) file format that encodes all of our examples.

While no performance issues of solvers for QP problems are considered in
this paper, we refer to the comprehensive benchmark site \url{http://plato.asu.edu/bench.html}.\todo[inline]{SV: Should one really point to this site? The benchmarks there are often faulty. Until recently, the SCIP 4 benchmark was using SCIP 3.1. Currently, the GAMS 25.0.2 benchmark partly uses 25.0.1. I wouldn't suggest anyone to take this site much serious.} Of the result on this site, three deal exclusively with
QP problems, namely the (1) large SOCP, (2) MISOCP, and the (3) MIQ(C)P benchmarks, while three others contain partial results for such problems,
namely those for (4) parallel barrier solvers on large LP/QP problems, (5) AMPL-NLP and (6) MINLP.
Benchmarks (1, 2 \& 4) contain only convex instances, while the others
include nonconvex ones. Global optima are obtained by several of the solvers in
benchmarks (3 \& 5), while all solvers in the latest addition (6) compute
global optima.
%, they are ANTIGONE,
%BARON, COUENNE, LINDO, and SCIP, c.f.~\S\ref{subsec:solver}.
Benchmark (6) is based on MINLPLib~2 \cite{Vigerske2014}, a
collection of currently 1527 instances. In order to give a first representative
impression of solver performance, care was taken there to reduce the number of
instances and allow all solvers to finish in a reasonable time.
More than half of the selected instances are QP or QCP.
%A time limit of two hours on a
%modern workstation with sufficient memory was used. Computations were done in
%GAMS with scripts derived from the SCIP check scripts and available at GitHub.
For details we refer to \url{http://plato.asu.edu/ftp/minlp.html}.
